Meta-analysis of fungicide application timing experiments for powdery mildew

### 2020-05-25 vignette/191115_PMMB_DataWrangling_PM.Rmd
Correct and document fold_data() code

## Import Libraries
```{r message=FALSE, warning=FALSE}
# install.packages("openxlsx")
# install.packages("readxl")
# install.packages("tidyr")
# install.packages("agricolae")

library(openxlsx)
library(readxl)
library(tidyr)
library(dplyr)
library(data.table)
library(agricolae)
library(here)

@@

## Functions
```{r functions}
fold_data <- function(new_DataFrame, template_DataFrame) {
   for (i in colnames(new_DataFrame)) {
      if (i == colnames(new_DataFrame)[1]) {
         x1 <- vector()
      }

@@

   new_DataFrame[cnames2[!(cnames2 %in% cnames1)]] <-
      NA # adding column names to new_DataFrame not in template_DataFrame
   new_DataFrame <-
      new_DataFrame[, c(cnames2, cnames1[is.na(x1)])]  # adding column names to new_DataFrame not in template_DataFrame
   return(new_DataFrame)
}
source(here("copy_class.R"))
source(here("R/data_mesh.R"))
```

>>>>

## Import Libraries
```{r message=FALSE, warning=FALSE}
library(openxlsx)
library(readxl)
library(tidyr)
library(dplyr)
library(data.table)
library(agricolae)
library(here)

@@

## Functions
```{r functions}
fold_data <- function(new_DataFrame, template_DataFrame) {
   # This function formats a dataframe to have the same column order as a template data.frame
   # If colums are missing from the new_DataFrame that are in the template_DataFrame, it creates them 
   # with NA values. 
   # Columns in the new_DataFrame, which are not in the template_DataFrame are appended to the right-hand-side
   # of the new_DataFrame
   # Using this function assists in joining the two data.frames together so colums are in the same order

   for (i in colnames(new_DataFrame)) {
      if (i == colnames(new_DataFrame)[1]) {
         x1 <- vector()
      }

@@

   new_DataFrame <- as.data.frame(new_DataFrame)

   new_DataFrame[,cnames2[!(cnames2 %in% cnames1)]] <-
      NA # adding column names to new_DataFrame which are in the template_DataFrame
   new_DataFrame <-
      new_DataFrame[, c(cnames2, cnames1[is.na(x1)])]  # adding columns to new_DataFrame not in template_DataFrame  # aranges column names to new_DataFrame not in template_DataFrame

   return(new_DataFrame)
}
source(here("R/copy_class.R"))
source(here("R/data_mesh.R"))
```
